Linear Vlasov Theory in the Shearing Sheet Approximation \\ with Application to the Magneto-Rotational Instability

### 2014-08-11 paper.tex
Renamed angle in Stix basis

\begin{figure}
  \centering
  \input{stix.tex}
  \caption{Illustration of the coordinate transformations
    \labelcref{eq:e3,eq:e12} used in calculating the plasma response tensor
    \labelcref{eq:response-tensor-gyrotropic}. The $(x,y,z)$-coordinate frame
    is the standard shearing sheet coordinate frame. The gyro-frequency vector
    $\vomg$ defines the $3$-axis of the $(1,2,3)$-coordinate frame that we
    refer to as the Stix frame. The $1$-axis is rotated with respect to the
    $x$-axis by an angle $\alpha$ about the $3$-axis, which in turn is
    inclined with respect to the $z$-axis by an angle $\varphi$ about the
    $x$-axis. The two Euler angles $\varphi$ and $\alpha$ are related through
    $k_x\tan\alpha=k_z\sin\varphi$.}\label{fig:stix}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{stix.tex}
  \caption{Illustration of the coordinate transformations
    \labelcref{eq:e3,eq:e12} used in calculating the plasma response tensor
    \labelcref{eq:response-tensor-gyrotropic}. The $(x,y,z)$-coordinate frame
    is the standard shearing sheet coordinate frame. The gyro-frequency vector
    $\vomg$ defines the $3$-axis of the $(1,2,3)$-coordinate frame that we
    refer to as the Stix frame. The $1$-axis is rotated with respect to the
    $x$-axis by an angle $\chi$ about the $3$-axis, which in turn is
    inclined with respect to the $z$-axis by an angle $\varphi$ about the
    $x$-axis. The two Euler angles $\varphi$ and $\chi$ are related through
    $k_x\tan\chi=k_z\sin\varphi$.}\label{fig:stix}
\end{figure}
